Proposed Solution

### 2017-04-18 OOPSLA17/secs/intro.tex
stuff

%what is the problem
Configuration errors (also known as misconfigurations) have become
one of the major causes of system failures, resulting in security vulnerabilities,
application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
In one high profile case,  
Facebook and Instagram became inaccessible~\cite{mashableNews}
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In another case, a system configuration change caused an outage of AT\&T's 911 service for five hours.
During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
These critical system failures are not rare -
a software system failures study~\cite{yin11anempirical},
reports that about 31\% of system failures were caused by 
configuration errors.
This is even higher than the percentage of failures resulting from program bugs (20\%).

@@

%what do we do
In this paper, we propose a framework for automated verification of configuration files: 
We derive specifications for a correct configuration file by processing a training set of configuration files that may contain some errors.
The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.

@@

In order to learn a specification from a large training set of configuration files,
the first step is to 
translate this training set into a more structured typed representation.
We then apply the learning process and we learn an abundant set of rules 
specifying various properties that hold on the given training set. The rules, in general, 
specify which properties keywords in configuration files need to satisfy.
The learning process is language-agnostic and works for any kind 
of configuration files, though all of the files in the training set need to be of 
the same language (such as MySQL or HTTPD configuration files).
This learning process is a way to derive a specification for configuration files. 
With the learned specification, \app can then efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.

>>>>

%what is the problem
Configuration errors (also known as misconfigurations) have become
one of the major causes of system failures, resulting in security vulnerabilities,
application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
In a recent high visible case~\cite{mashableNews},  
Facebook and Instagram became inaccessible
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In another case, a system configuration change caused an outage of AT\&T's 911 service for five hours.
During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
These critical system failures are not rare -
a software system failures study~\cite{yin11anempirical},
reports that about 31\% of system failures were caused by 
configuration errors.
This is even higher than the percentage of failures resulting from program bugs (20\%).

@@

%what do we do
In this paper, we propose a framework for automated verification of 
configuration files, which mimics standard automated verification 
techniques: for a given configuration file, we  checked if it 
adheres to a specification, and if there are issues we report them to 
the user.

@@

Our main task was to first derive a specification for configuration 
files. We first process a \ruzica{mention the size, size does matter :)}training set of configuration files. Those files are benchmarks 
available on-line~\ruzica{put a citation here}. They are mostly correct
but they also may contain some errors.

In order to learn a specification from this large set of configuration
files,
the first step is to 
translate the training set into a more structured typed representation.
We then apply the learning process and we learn an abundant set of rules 
specifying various properties that hold on the given training set. 
\ruzica{say here 2 sentences about the learning process }

The rules, in general, 
specify which properties keywords in configuration files need to satisfy.
The learning process is language-agnostic and works for any kind 
of configuration files, though all of the files in the training set need to be of 
the same language (such as MySQL or HTTPD configuration files).

This learning process is a way to derive a specification for configuration files. 
With the learned specification, \app can then efficiently check 
the correctness of the configuration files of interest and detect 
potential errors. Errors are reported if the configuration file does not 
adhere to the derived specification.

The errors that we learn are detailed and complex enough proactively report a wide range of potential misconfigurations.
In this framework, the example configurations from which we derive the specifications do not need to be labeled as correct or incorrect.
